Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-06-18 article.tex
LNCS 12 pages + appendix

\author{%
	Both Emerite Neou\thanks{On a Co-tutelle  Agreement with the Department of Mathematics of the University of Trento}\inst{1}
  Romeo Rizzi\inst{2} \and
  St\'ephane Vialette\inst{1}
}% end author
\institute{%
	Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC,
	F-77454, Marne-la-Vallée, France\\
  \email{\{neou,vialette\}@univ-mY.fr}
  \and
  Department of Computer Science,
  Università degli Studi di Verona, Italy \\
  \email{romeo.rizzi@univr.it}
}% end institute

@@

A way to understand this lemma is if two ascent (resp. decsent) elements
need to occur in consecutive elements in value then every element in $\pmotif$ which are between those two elements (if any) are descent (resp. ascent) elements.

>>>>

\author{%
	Both Emerite Neou\thanks{On a Co-tutelle  Agreement with the Department of Mathematics of the University of Trento}\inst{1}
  Romeo Rizzi\inst{2} \and
  St\'ephane Vialette\inst{1}
}% end author
\institute{%
	Universit\'e Paris-Est, LIGM (UMR 8049), CNRS, UPEM, ESIEE Paris, ENPC,
	F-77454, Marne-la-Vallée, France\\
  \email{\{neou,vialette\}@univ-mlv.fr}
  \and
  Department of Computer Science,
  Università degli Studi di Verona, Italy \\
  \email{romeo.rizzi@univr.it}
}% end institute

@@

According to the above lemma,
if two ascent (resp. decsent) elements
have to occur in consecutive elements in value then every element in 
$\pmotif$ which are between those two elements (if any) are descent (resp. ascent) 
elements.
